Modelling last glacial cycle ice dynamics in the Alps

### 2018-08-17 articles/cycle/response-editor3.tex

    \referee{\textbf{p.~15, l.~31:}
        `simulation' (not sumulation)}

    Done.

    \referee{\textbf{p.~16, l.~12:}
        `Fig. 5' has nothing to do with `reviews', what do you mean with `Fig.
        5 for reviews'???}

    With ``cf.~\citealp[Fig.~5 for reviews]{Ivy-Ochs.2015, Wirsig.etal.2016}'',
    we meant to refer to Fig.~5 in the paper by \citep{Wirsig.etal.2016}. We
    have removed ``Fig.~5'' in this particular instance.

@@

    \referee{\textbf{p.~23, l.~1:}
        is it not rather `glacier physics' as the till is not ice (or ice and
        glacier physics).}

    Correct. We have changed to ``glacier physics''.

% ----------------------------------------------------------------------

\sechead{New references}

    References to several new papers were added \citep{Cohen.etal.2018,
    Gild.etal.2018, Ivy-Ochs.etal.2018, Barrett.etal.2018, Spotl.etal.2018}.

### 2018-08-17 articles/cycle/alps-cycle.tex
Add newly published references from 2018.

    The timing of the LGM has been documented by radiocarbon and cosmogenic
    isotope dating techniques at multiple locations around the Alps (cf.
    \citealp{Ivy-Ochs.2015};
    \citealp{Wirsig.etal.2016} for reviews; and the more recent
    publications by \citealp{Monegato.etal.2017, Federici.etal.2017}). These
    data indicate that Alpine glaciers reached their maximum extent between 26
    and 20\,ka (calibrated \chem{^{14}C} and \chem{^{10}Be} ages), but also
    that terminal lobes stayed in the foreland until 22\,ka to 17\,ka,
    when they experienced rapid retreat synchronously to lowering of the ice
    surface in the mountains (\citealp{Ivy-Ochs.2015};
    \citealp[Fig.~5]{Wirsig.etal.2016}; \citealp[Fig.~3]{Monegato.etal.2017}).

@@

    Glacial history of the Alps prior to the LGM remains poorly constrained.
    Although the four glaciations model \citep{Penck.Bruckner.1909} has long
    been used, it is now known that glaciers advanced onto the foreland at
    least 15 times since the beginning of the Quaternary at 2.58\,Ma
    \citep{Schluchter.1991, Preusser.etal.2011}. Sparse geological
    data indicate that the last glacial cycle may have comprised two or even
    three periods of glacier growth and decay \citep{Preusser.2004, Ivy-Ochs.etal.2008}.
    Luminescence dating from two sites in the central northern foreland
    indicate an early last glacial advance of Alpine glaciers onto the near
    foreland around $107\pm9$ to $101\pm5$\,ka \citep{Preusser.etal.2003,
    Preusser.Schluchter.2004}. Evidence for a MIS~4 glaciation is equally
    sparse \citep[Sect.~\ref{sec:footprints};][]{Keller.Krayss.2010,
    Barrett.etal.2017, Haldimann.etal.2017}, and its timing remains uncertain
    \citep[e.g.,][]{Link.Preusser.2006, Preusser.etal.2007}.

>>>>

    The timing of the LGM has been documented by radiocarbon and cosmogenic
    isotope dating techniques at multiple locations around the Alps (cf.
    reviews by \citealp{Ivy-Ochs.2015, Wirsig.etal.2016}; and the more recent
    publications by \citealp{Federici.etal.2017, Monegato.etal.2017,
    Gild.etal.2018, Ivy-Ochs.etal.2018}). These
    data indicate that Alpine glaciers reached their maximum extent between 26
    and 20\,ka (calibrated \chem{^{14}C} and \chem{^{10}Be} ages), but also
    that terminal lobes stayed in the foreland until 22\,ka to 17\,ka,
    when they experienced rapid retreat synchronously to lowering of the ice
    surface in the mountains (\citealp{Ivy-Ochs.2015};
    \citealp[Fig.~5]{Wirsig.etal.2016}; \citealp[Fig.~3]{Monegato.etal.2017}).

@@

    Glacial history of the Alps prior to the LGM remains poorly constrained.
    Although the four glaciations model \citep{Penck.Bruckner.1909} has long
    been used, it is now known that glaciers advanced onto the foreland at
    least 15 times since the beginning of the Quaternary at 2.58\,Ma
    \citep{Schluchter.1991, Preusser.etal.2011}. Sparse geological
    data indicate that the last glacial cycle may have comprised two or even
    three periods of glacier growth and decay \citep{Preusser.2004, Ivy-Ochs.etal.2008}.
    Luminescence dating from two sites in the central northern foreland
    indicate an early last glacial advance of Alpine glaciers onto the near
    foreland around $107\pm9$ to $101\pm5$\,ka \citep{Preusser.etal.2003,
    Preusser.Schluchter.2004}. Evidence for a MIS~4 glaciation is equally
    sparse \citep[Sect.~\ref{sec:footprints};][]{Keller.Krayss.2010,
    Barrett.etal.2017, Haldimann.etal.2017}, and its timing remains uncertain
    \citep[e.g.,][]{Link.Preusser.2006, Preusser.etal.2007}. During MIS~3,
    major Eastern Alpine valleys hosted wolly mammoths \citep{Spotl.etal.2018}
    and open vegetation \citep{Barrett.etal.2018}, indicating more restricted
    glaciation.
